---
title: "Lab 00 - Hello IDS!"
author: "LuckyLuke13"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Marcel", "Edwin", "Josh", "Kenny", "Luke"),
  github_username = c("marcel237", "edivan05", "jm-56", "kenny-webb", "dethbringer"), 
  colour = c("red", "blue", "orange", "green", "red"),
  hobby = c("gambling", "card tricks", "football", "hill walking", "writing"),
  favourite_number = c(7,5,3,6,3)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The data shows most people liked higher numbers within 1-10

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Username", 
          y = "Favourite number",
          title = "Graph showing the my group's favourite numbers")
```

The graph shows most people liked higher numbers within 1-10

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

The data could maybe be put in a pie chart?  


